Report on a Safety Checker for Petri nets

### 2013-11-18 paper/workspace/main.tex
Updated paper
Added benchmark tables to report

* Assignment A:
  nc  = 1
  m1  = 0
  m2  = 0
  cs1 = 1
  cs2 = 1
  t1  = 1
  t2  = 1
  t3  = 0
  t4  = 0

* Trap conditions C_\theta:
 TODO

* Assignment A_\theta:
 TODO

* Constraint \delta:
 TODO
\end{verbatim}

@@

\end{document}

>>>>

* Assignment A:
  nc  = 0
  m1  = 0
  m2  = 0
  cs1 = 1
  cs2 = 1
  t1  = 1
  t2  = 1
  t3  = 0
  t4  = 0

* Trap conditions C_\theta:
  nc  => t1 /\ t2
  m1  => t1 /\ t2
  m2  => t1 /\ t2
  cs1 => t3
  cs2 => t4

  t1  => m2 \/ cs1
  t2  => m1 \/ cs2
  t3  => m1 \/ nc
  t4  => m2 \/ nc

  nc \/ m1 \/ m2

  ~cs1 /\ ~cs2

* Assignment A_\theta:
  nc  = false
  m1  = true
  m2  = true
  cs1 = false
  cs2 = false

  t1  = true
  t2  = true
  t3  = true
  t4  = true

* Constraint \delta:
  m1 + m2 >= 1
\end{verbatim}

@@

\section{Benchmarks of \bfc}

We experimented on the benchmarks \ttt{cprover-PN} and
\ttt{cprover\_software\_analysis}
available at
\ttt{http://www.mpi-sws.org/\~{}jkloos/iic-experiments/cprover.zip}.
The set of benchmarks consists 77 benchmarks, 26 positive and 51 negative.
We applied 8 tool configurations to the set of benchmarks.
Table~\ref{bfc-experiments} shows the corresponding experimental results.

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | r | p{7cm} | r | r | r | r | } %
    \hline
    \multicolumn{2}{|l|}{Configuration} & pos & neg & don't know & TO \\
    \hline
    C1 & State constraint over real numbers & 23 &  0 & 54 &  0 \\
    C2 & State constraint over integers        & 23 &  0 & 54 &  0 \\
    \hline
    C3 & C2 + TrapConditions                   & 23 &  0 & 54 &  0 \\
    C4 & C3 + SubnetTrapConditions         & 23 &  0 & 50 &  4 \\
    C5 & C4 + EmptyTrapConditions          & 23 &  0 & 46 &  8 \\
    \hline
    C6 & C1 + state space exploration \& TO 1\,min & 26 & 34 & 0 & 17 \\
    C7 & C1 + state space exploration \& TO 10\,min & 26 & 39 & 0 & 12 \\
    C8 & C1 + state space exploration \& TO 8\,h   & 26 & 45 & 0 &  6 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \bfc}
\label{bfc-experiments}
\end{table}

Observations:
\begin{itemize}
\item State constraints over integers or reals correctly determine that the 23 benchmarks in Appendix~\ref{bfc-experiments-c1} are positive.
\item Composing state space constraints with concrete state space
  exploration gives the following 3 additional positives.
\begin{verbatim}
cprover-PN/lamport
cprover-PN/newdekker
cprover-PN/peterson
\end{verbatim}
\end{itemize}

\newpage

\section{Benchmarks of \mist}

We experimented on the benchmarks available at \\
\ttt{https://github.com/pierreganty/mist/tree/master/examples/boundedPN}
and \\
\ttt{https://github.com/pierreganty/mist/tree/master/examples/PN}.
The set of benchmarks consists 27 benchmarks, 23 positive and 4 negative.
We applied 6 tool configurations to the set of benchmarks.
Table~\ref{mist-experiments} shows the corresponding experimental results.

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | r | p{6cm} | r | r | r | r | }
    \hline
    \multicolumn{2}{|l|}{Configuration} & pos & neg & don't know & TO \\
    \hline
    C1 & State constraint with real numbers & 14 &  0 & 13 &  0 \\
    C2 & State constraint with integers     & 14 &  0 & 13 &  0 \\
    \hline
    C3 & C2 + TrapConditions               & 20 &  0 &  7 &  0 \\
    C4 & C3 + SubnetTrapConditions         & 21 &  0 &  6 &  0 \\
    C5 & C4 + EmptyTrapConditions          & 21 &  0 &  6 &  0 \\
    \hline
    C9 & C4 + state space exploration \& TO 4\,h & 21 &  2 & 0 &  4 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \mist}
\label{mist-experiments}
\end{table}

Observations:
\begin{itemize}
\item State constraints over integers or reals correctly determine that the 14 benchmarks in Appendix~\ref{mist-experiments-c1} are positive.
\item Composing state constraints with TrapConditions gives the following 6 additional positives.
\begin{verbatim}
PN/pingpong
PN/basicME
PN/multiME
boundedPN/lamport
boundedPN/newdekker
boundedPN/peterson
\end{verbatim}
\item Composing state constraints with TrapConditions and SubnetTrapConditions gives the additional positive \ttt{PN/manufacturing}.
  \item The remaining positive benchmarks are the following.
\begin{verbatim}
PN/extendedread-write
PN/extendedread-write-smallconsts
\end{verbatim}
\end{itemize}
\end{document}
